Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-03 paper.tex
done with Uncertainty measurement section

@@

 Packae   & Facility   & Parameters                \\
 \midrule
 Cycamore & Enrichment & Tail Assay                \\
          & Separation & Separation efficiency     \\
          & Storage    & Residence Time            \\
 \midrule
 CyCLASS  & Reactor    & Cycle Length              \\
          &            & Power                     \\
          &            & Fuel Enrichment (PWR-UOX) \\

@@

\section{The Experiment}

>>>>

\usepackage[acronym]{glossaries}
\newacronym{UOX}{UOX}{uranium oxide fuel}
\newacronym{MOX}{MOX}{mixed oxide fuel}
\newacronym{LWR}{LWR}{light water reactor}
\newacronym{FBR}{FBR}{fast breeder reactor}

@@

Package   & Facility   & Parameters                \\
\midrule
Cycamore & Enrichment & Tail Assay                \\
         & Separation & Separation efficiency     \\
         & Storage    & Residence Time            \\
\midrule
CyCLASS  & Reactor    & Cycle Length              \\
         &            & Power                     \\
         &            & Fuel Enrichment (PWR-UOX) \\

@@

\section{The Experiment}
\subsection{The Fuel Cycle}
This work aims to assess the impact of the functional uncertainties of a
simple transition (see Figure \ref{fig:cycle}) inspired from the EG23 of the Screening And
Evaluation Group\cite{FCO}: a transition from light water reactors fleet loaded
with \glspl{UOX} fuel to a sodium fast reactors fleet loaded \glspl{MOX} fuel, considering an
$1\%/$y grows of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with in green each operational parameters associated with an
  uncertainty.}\label{fig:cycle}
\end{figure}

As illustrated on Figure \ref{fig:power}, the transition starts with a fleet
fully composed by \glspl{LWR} loaded with enriched \glspl{UOX} fuel. The actual
transition starts around year 35, with the deployment of \glspl{FBR}, loaded
with Mixed oxide fuel (MOX), consisting of plutonium blended with natural
uranium. Once the transition to a full \glspl{FBR} fleet is completed, the
\glspl{FBR} fleet is slowly replaced with \glspl{FBR} with a lower breeding
ratio.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.32]{power.png}
  \caption{Electric power generated over time, with in blue the full production,
      in orange the \glspl{LWR} contribution, in green the hight breeding ratio
    \glspl{FBR} and in red the low breeding ratio \glspl{FBR}.}
    \label{fig:power}
\end{figure}

The plutonium, required for the \glspl{MOX} fabrication, is reprocessed
from all used fuel, at first only used UOX, then used MOX fuel as they start to
be available for reprocessing.

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed materials availabilities). The enrichment of the UOX is processed on
demand. Buffer storages (not shown on Figure \ref{fig:cycle}) is present between
all facilities with constant processing rates.

\subsection{Uncertainty Measurements}
In this specific study, one will only focus on the uncertainty on the produced
electric power as a function of time, on the total quantity of natural uranium
used and on the total unused fissile inventory (unused reprocessed plutonium).
In order to estimate the total uncertainty on those 3 parameters as well as the
individual contribution of the operational parameters several set of (199) simulations
have been completed.

In addition to the set with all parameters are sampled according to their
uncertainty, a set a have been computed for each parameter, with all the other
remaining fixed to the reference value.
